---
title: "HW6"
author: "Soungbin Yim"
date: "2022-11-29"
output: github_document
---
### Due date

Due: December 3 at 11:59pm. 

### Points

| Problem         | Points    |
|:--------------- |:--------- |
| Problem 0       | 20        |
| Problem 1       | --        |
| Problem 2       | 40        |
| Problem 3       | 40        |


### Problem 0

This "problem" focuses on structure of your assignment, including the use of R Markdown to write reproducible reports, the use of R Projects to organize your work, the use of relative paths to load data, and the naming structure for your files. 

To that end: 

* create a public GitHub repo + local R Project for this assignment
* write solutions using a .Rmd file that outputs a `github_document` / .md file
* submit a link to your repo via Courseworks

Your solutions to Problems 1 and 2 should be implemented in your .Rmd file, and your git commit history should reflect the process you used to solve these Problems. 

For Problem 0, we will assess adherence to the instructions above regarding repo structure, git commit history, and whether we are able to knit your .Rmd to ensure that your work is reproducible. Adherence to appropriate styling and clarity of code will be assessed in Problems 1+ using the homework [style rubric](homework_style_rubric.html). 

This homework includes figures; the readability of your embedded plots (e.g. font sizes, axis labels, titles) will be assessed in Problems 1+.

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(patchwork)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1


## Problem 2
The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here. You can read their accompanying article here.

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.
```{r}
homicide_df =
  read_csv("./homicide-data.csv") %>%
  mutate(
    victim_age = recode(victim_age,"Unknown" = ""),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White"),
    city_state = str_c(city, ", ", state), 
    resolved = as.numeric(disposition == "Closed by arrest"),
  ) %>%
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) &
         victim_race %in% c("White", "Black")
  )
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city == "Baltimore") %>% 
  select(resolved, victim_age, victim_race, victim_sex)

```

```{r}
fit_logistic = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         LCL = exp(estimate - 1.96*std.error),
         UCL = exp(estimate + 1.96*std.error)) %>%
  select(term, log_OR = estimate, OR, LCL, UCL) %>% 
  knitr::kable(digits = 3)
```


Based on the table, the estimated odds ratio of having homicide solved between male and female victims is 0.426, adjusting for victim age and race, in Baltimore, MD. We are 95% confident that the true odds ratio of having homicide solved between male and female victims lies between 0.325 and 0.558, adjusting for victim age and race, in Baltimore, MD. 


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}
city_glm = 
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    models = map(data, ~glm(resolved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())),
    results = map(models, broom::tidy)
    ) %>%
  select(city_state, models, results) %>%
  unnest(cols = results) %>%
  filter(term == "victim_sexMale") %>%
  mutate(
    OR = exp(estimate),
    LCL = exp(estimate - 1.96*std.error),
    UCL = exp(estimate + 1.96*std.error)
  ) %>%
   select(city_state, OR, LCL, UCL)
  
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
city_glm %>% 
  ggplot(aes(reorder(city_state, OR), OR)) + 
  geom_point(aes(color = city_state)) + 
  geom_errorbar(aes(ymin = LCL, ymax = UCL)) +
   labs(
    title = "Problem 2, plot of Adjusted OR and CI for solving homicides comparing male victims to female victims In each city ",
    x = "City, State",
    y = "Adjusted OR") +
   theme(axis.text.x = element_text(angle = 90),
         legend.position = "none")
```

Based on the plot, we can see the majority of adjusted ORs have their values and upper CI below 1, meaning most of cities' male victims have smaller odds of solved homicide case than females. Many of ORs in the plot do not contain the null value of 1, meaning they are not significant. 

## Problem 3
Loading and cleaning the data for the analysis, checking if there is any missing data

```{r}
birth_wt <- read.csv("./birthweight.csv") %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform),
         id = row_number())

str(birth_wt)
sapply(birth_wt, function(x) sum(is.na(x)))
```

`babysex`, `frace`, `mrace` were converted to factor variables, and there was no missing values in the dataframe.



Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
birth_wt %>% 
  ggplot(aes(x = bwt)) + 
  geom_histogram(binwidth = 25) + 
  labs(
    title = "Checking Assumption", x = "Birthweight (g)",y = "Count"
  )
```

Looking at the histogram, 'birth_wt' has relatively normal distribution. 

I decided to exclude 'pnumlbw' and 'pnumgsa' 'malform' and 'parity' because they all have no observation or almost no observation, and 'ppbmi' because I decided to use 'ppwt' instead. 

#### Building the full model

```{r}
full_model = 
  lm(
    bwt ~ babysex + bhead + blength + delwt+ fincome+frace + gaweeks + menarche+ mheight + momage + mrace + smoken + ppwt + wtgain,
    data = birth_wt
  )
```

#### Summary table to see which covariates have p<0.05 to come up with reduced model

```{r}
summary(full_model) %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
   mutate(
    p_value = format.pval(p.value, digits = 3, eps = 0.05)
  ) %>% 
  select(-p.value) %>%
  arrange(p_value) %>% 
  knitr::kable()
```

The significant variables based on the table were 'babysex2', 'bhead', 'blength', 'delwt', 'gaweeks', 
'mheight', 'mrace2', 'smoken', and 'ppwt'. 

#### reduced model
```{r}
reduced_model = 
  lm(
    bwt ~ babysex + bhead + blength + delwt+ gaweeks +  mheight + mrace + smoken + ppwt,
    data = birth_wt
  )
birth_wt %>% 
  add_predictions(reduced_model) %>% 
  add_residuals(reduced_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  labs(
    title = "Residuals against Fitted Values",
    x = "Fitted Values",
    y = "Residuals"
  )
```

Based on the plot created, the homoscedasticity assumptions seems to be violated. Also, the there are some notable outliers. To resolve these issues, few things can be done. We can include creating a formal rule for the exclusion of outliers, or fitting a model that is robust to outliers.



Compare your model to two others:

1) One using length at birth and gestational age as predictors (main effects only)

2) One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.

```{r}
 crossv_mc(birth_wt, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
    current_mod = map(train, ~gam(bwt ~ s(wtgain) + s(delwt), data = .x)),
    other_mod_1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    other_mod_2  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_current = map2_dbl(current_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mod_1 = map2_dbl(other_mod_1, test, ~rmse(model = .x, data = .y)),
    rmse_mod_2 = map2_dbl(other_mod_2, test, ~rmse(model = .x, data = .y))) %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Based on the plots that I created above, the reduced model has the lowest mean value of rmse, meaning it may be the best fitted model among three models. 



